Physics of Tidal Dissipation in Early-Type Stars and White Dwarfs: Hydrodynamical Simulations of Internal Gravity Wave Breaking in Stellar Envelopes

### 2020-04-05 writeups/Su_IGW_break.tex
check in colorblind plots, need to update captions

For the weakly forced simulation, we expect
$A_i(t) = 1$ when integrated between the forcing and damping zones, i.e.\
$z_b \gtrsim z_0$ and $z_t \lesssim z_T$ ($z_0, z_T$ are defined in
Eq.~\eqref{eq:vol_drive} and Eq.~\eqref{eq:Gamma} respectively). For consistency
with the nonlinear case later, we choose $z_b = z_0 + 3\sigma$ and $z_t = z_b +
H$. Note that using a larger integration domain by choosing $z_t = z_T - \Delta
z$ just below the upper damping zone instead does not change the measured $A_i$.
The resulting measurement of $A_i(t)$ is shown in Fig.~\ref{fig:lin_amps}, and
indeed $A_i \approx 1$ after the initial transient.
\begin{figure}
    \centering
    \includegraphics[width=0.9\columnwidth]{plots/lin_amps.png}
    \caption{Amplitude of the excited IGW over time (in units of $N^{-1}$) in
    the weakly forced simulation, computed using Eq.~\eqref{eq:ahat_def}.
    $A_i(t) = 1$ corresponds to perfect agreement with the analytical estimate.
    After an initial transient phase, we observe $A_i(t)$ asymptotes to $\approx
    1$, implying continuous excitation of identical IGW with the expected
    amplitude. The small deviation of $A_i(t)$ from unity may be due to
    timestepping errors, as a relatively large fixed step size $\Delta t =
    0.1/N$ was used for this simulation.}\label{fig:lin_amps}
\end{figure}

@@

    \includegraphics[width=0.45\textwidth]{plots/yubo_000134_labeled.png}\hfil
    %
    \includegraphics[width=0.45\textwidth]{plots/yubo_000451_labeled.png}
    \caption{Snapshots of $u_x$ and $\Upsilon \equiv \ln \p{\rho / \bar{\rho}}$
    in the fiducial simulation illustrating distinct phases of the evolution of
    the flow. Damping layers are shaded in light grey (see
    Section~\ref{ss:damping}), while the forcing zone (see
    Section~\ref{ss:forcing}) is shaded in light green (boundaries are at $z_0
    \pm 3\sigma$). The four panels illustrate (i) the initial transient wave
    breaking phase, (ii) formation of a distinct critical layer, (iii)
    steepening of the critical layer, and (iv) downward advance of the critical
    layer.}\label{fig:snapshots}
\end{figure*}

>>>>

For the weakly forced simulation, we expect
$A_i(t) = 1$ when integrated between the forcing and damping zones, i.e.\
$z_b \gtrsim z_0$ and $z_t \lesssim z_T$ ($z_0, z_T$ are defined in
Eq.~\eqref{eq:vol_drive} and Eq.~\eqref{eq:Gamma} respectively). For consistency
with the nonlinear case later, we choose $z_b = z_0 + 3\sigma$ and $z_t = z_b +
H$. Note that using a larger integration domain by choosing $z_t = z_T - \Delta
z$ just below the upper damping zone instead does not change the measured $A_i$.
The resulting measurement of $A_i(t)$ is shown in Fig.~\ref{fig:lin_amps}, and
indeed $A_i \approx 1$ after the initial transient.
\begin{figure}
    \centering
    \includegraphics[width=0.9\columnwidth]{plots/lin_amps.png}
    \caption{Amplitude of the excited IGW over time (in units of $N^{-1}$) in
    the weakly forced simulation, computed using Eq.~\eqref{eq:ahat_def}.
    $A_i(t) = 1$ corresponds to perfect agreement with the analytical estimate.
    After an initial transient phase, we observe $A_i(t)$ asymptotes to $\approx
    1$, implying continuous excitation of identical IGW with the expected
    amplitude. The small deviation of $A_i(t)$ from unity may be due to
    \textcolor{Corr}{truncation error in our implicit timestepping scheme}, as a
    relatively large fixed step size $\Delta t = 0.1/N$ was used for this
    simulation.}\label{fig:lin_amps}
\end{figure}

@@

    \includegraphics[width=0.45\textwidth]{plots/yubo_000134_labeled.png}\hfil
    %
    \includegraphics[width=0.45\textwidth]{plots/yubo_000451_labeled.png}
    \caption{Snapshots of $u_x$ and $\Upsilon \equiv \ln \p{\rho / \bar{\rho}}$
    in the fiducial simulation illustrating distinct phases of the evolution of
    the flow. \textcolor{Corr}{See the online PDF for a color version.} Damping
    layers \textcolor{Corr}{at the top and bottom of the simulation domain} are
    shaded in light grey (see Section~\ref{ss:damping}), while the forcing zone
    \textcolor{Corr}{in the lower middle portion of the simulation domain} (see
    Section~\ref{ss:forcing}) is shaded in light green (boundaries are at $z_0
    \pm 3\sigma$). The four panels illustrate (i) the initial transient wave
    breaking phase, (ii) formation of a distinct critical layer, (iii)
    steepening of the critical layer, and (iv) downward advance of the critical
    layer.}\label{fig:snapshots}
\end{figure*}
